---
title: "Collaborative Learning Event Feedback Report"
author: "NIHR CLAHRC NWL Coding Club"
date: "14 May 2018"
output:
  beamer_presentation: default
  slidy_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
```

```{r}
source('../R/clean-reg-data.R')
source('../data-raw/load_raw_data.R')
source('../R/merge_dataframes.R')
source('../R/linegraph_eventdate_attendance.R')
filenames<-Sys.glob("../data-raw/REG_Report_*.xlsx")
data_frames <- load_REG_files(filenames)
merged_datatable<-rbindlist(data_frames)
#str(merged_datatable)
```

<!--# Registration analysis -->

## Number of registrations over time

*SPC chart showing how many people registered for each event over time*


```{r reg_graph, results='asis', fig.height=5, fig.width=7}
plot_reg_no(df = merged_datatable)
```



## Registrations by host organisation

*Visualisation of distribution of host organisations of those registered*

## Registrations by role

*Visualisation of distribution of roles of those registered*

## Registrations by CLAHRC theme

*Visualisation of distribution of themes those registered identified with*

<!--# Attendance analysis
*Note: cannot do this section from data imported to date* -->

## CL Event Attendance

## CL Event Attendance and feedback response rates

## CL Event feedback response rates

## What primary perspective or background are you bringing to this event? (feedback forms)

## Which of the following are you involved with? (Please select all that apply)

## How long have you been involved with CLAHRC NWL?

## Please rate how useful you found the event as a whole

## Usefulness over CLAHRC 2

## Highlights

*This slide to be manually edited for each event*

## Wordles

## Quotes

## What could have been better?

## *More quotes to finish*

